---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OrgSeg

<!-- badges: start -->
[![R-CMD-check](https://github.com/Metacodon/OrgSeg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Metacodon/OrgSeg/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of OrgSeg package is to make the use of OrganoSeg analysis software easier. From importing and pre-processing of the raw excel file from the software to running analysis and plotting figures.

## Installation

You can install the development version of OrgSeg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Metacodon/OrgSeg")
```

## Example

Here is an example of running an analysis.

Read the OrganoSeg software output excel file:

```{r}
library(OrgSeg) # Load the package
file_path = system.file("extdata", "test_data.xls", package = "OrgSeg") # Path to the OrganoSeg output excel file. Here we've provided an example data file included in the package that you can access the path with system.file("extdata", "test_data.xls", package = "OrgSeg").
data <- read_excel_file(file_path)
```

Read the experiment information .csv file and extract the treatments and related indices into a list:

```{r}
exp_info_path = system.file("extdata", "exp_info.csv", package = "OrgSeg") # Path to the experiment information .csv file. Here we've provided an example experiment information .csv file included in the package that you can access the path with system.file("extdata", "test_data.xls", package = "OrgSeg").
exp_info_list <- read_exp_info(exp_info_path)
```

Create a merged tibble of all data with 3 columns of Area, Replicate, and Treatment:

```{r}
all_data <- tibbleing_loop (data, exp_info_list$index_list, exp_info_list$treatments)
```

Create a summary table to evaluate experiment controls:

```{r eval=FALSE}
ctrl_summary_table <- ctrl_table(all_data)
```
