---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OrgSeg

<!-- badges: start -->
[![R-CMD-check](https://github.com/Metacodon/OrgSeg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Metacodon/OrgSeg/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of OrgSeg package is to make the use of OrganoSeg analysis software easier. From importing and pre-processing of the raw excel file from the software to running analysis and plotting figures.

## Installation

You can install the development version of OrgSeg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Metacodon/OrgSeg")
```

## Example

Here is an example of running an analysis. Read and import the OrganoSeg software output excel file as following:

```{r}
library(OrgSeg) # Load the package
file_path = system.file("extdata", "test_data.xls", package = "OrgSeg") # Path to the OrganoSeg output excel file. Here we've provided an example data file included in the package that you can access the path with system.file("extdata", "test_data.xls", package = "OrgSeg").
data <- read_excel_file(file_path)
```

Read the experiment information .csv file and extract the treatments and related indices into a list:

```{r}
exp_info_path = system.file("extdata", "exp_info.csv", package = "OrgSeg") # Path to the experiment information .csv file. Here we've provided an example experiment information .csv file included in the package that you can access the path with system.file("extdata", "test_data.xls", package = "OrgSeg").
exp_info_list <- read_exp_info(exp_info_path)
```

Create a merged tibble of all data with 3 columns of Area, Replicate, and Treatment:

```{r}
all_data <- tibbleing_loop (data, exp_info_list$index_list, exp_info_list$treatments)
```

Create a summary table to evaluate experiment controls:

```{r eval=FALSE}
ctrl_table(all_data)
```

Based on the summary table, define the breaks and tags as following:

```{r}
breaks <- c(0,427,848,1869,50000) # Min/NegCtrl 3rd Qu./DMSO Mean/PosCtrl 3rd Qu./Max
tags <- c("noise","small organoids","medium organoids","large organoids")
```

Create a table to inspect bins for controls:

```{r eval=FALSE}
inspect_bins_table(all_data, breaks, tags)
```

Create a plot to inspect bins for controls:

```{r eval=FALSE}
inspect_bins_plot(all_data, breaks, tags)
```

Adjust the brakes if needed and inspect the table and plot again, if your happy you can continue.

